%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Modified by: Matthew Knight
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
		\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{\small#3} & \textit{\small #4} \\
		\end{tabular*}
	\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://sourabhbajaj.com/}{\Large Matthew Knight}} &
		\href{mailto:mgk1795@gmail.com}{mgk1795@gmail.com}\\
	\href{https://github.com/matt1795}{https://github.com/matt1795} & 
	 778-791-4069 \\
\end{tabular*}


%
%--------PROGRAMMING SKILLS------------
\section{}

Hey Donny,

\vspace{1 em}

I'm writing to continue the short conversation we had at the Expo on Friday, and
in response to Argus's Firmware Developer job posting.

\vspace{1 em}

I've been able to work on a large range of different types of software from
firmware, to operating systems, databases, and APIs. I've found that my passion
is developing applications using C++ and working with Embedded Linux.  I already
have experience working with Argus products, understand some of internal needs
of the company like production, and I love the people there.

\vspace{1 em}

Since working at Argus, I've been able to get my hands dirty with different
projects.  For my capstone, my team and I created a prototype for a scoliosis
brace wear-time tracker. This involved mechanical, hardware, and firmware design
for the wireless sensor, and we designed a messaging architecture that
transfered data from the sensor to a centralized server that would then provide
a UI to an orthopedic clinic. To do this we used mostly JavaScript based
technologies for the prototyping speed they offered. Currently my team and I are
continuing the project and working with our sponsor.  To make the system
production worthy, we are implementing the entire system in C++ and interfacing
with technologies like Bluetooth Low Energy, MQTT, PostgreSQL, and HTTP.

\vspace{1 em}

While I was finishing my last year at BCIT, I was working part-time for
Plasmatic Technologies. Initially the work involved reverse-engineering a
Honeywell serial protocol used in home security systems so that they could be
interfaced with. Later on I was able to work on compiling the Linux kernel to
add device drivers, working with their AWS backend, and overhauled a React
Native-based mobile app to get it to a point where it could be used in
production. By this point, the company had decided to drop the hardware platform
and so it was time for me to move onto something that better fit my passion and
skill set.

\vspace{1 em}

I'm currently working at Avigilon and it has been awesome. My team develops and
manages the Embedded Linux distribution that runs on servers at the center of
Avigilon's security system. By the time I joined the team, they had taken over a
C++ library that takes trained neural networks, accelerates the calculations
using GPU hardware, and handles passing around all the proprietary metadata.
I've learned a great deal taking part in the modernization of the library; most
of the work I've contributed has been adding a developer-friendly debugging
system as well as performance measurement at different points in the library to
validate latency and throughput improvements.

\vspace{1 em}

As for my mentioning of wanting to work remotely, I do know that there is a
hardware component to the position and it's important to be on-site for some of
the work. Ideally for me, I would work on-site until August and then begin to
transition to a remote position, coming in for meetings and any hands on work
that needs to be done. That being said, this is an ideal situation from my end,
and I'm open to talk about it.

\vspace{1 em}

Scott put decades of development into Argus and it's a fascinating project to
take that work and bring it into the C++ realm.  I'm excited to tackle this
challenge and to be a part of a company I care about.  Let's talk about the work
in more detail and how I'd be beneficial to the project. You can contact me by
phone at 778-791-4069; or by e-mail mgk1795@gmail.com.

\vspace{2 em}
Cheers,

Matt Knight

\end{document}
