%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Modified by: Matthew Knight
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
		\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{\small#3} & \textit{\small #4} \\
		\end{tabular*}
	\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://sourabhbajaj.com/}{\Large Matthew Knight}} &
		\href{mailto:mgk1795@gmail.com}{mgk1795@gmail.com}\\
	\href{https://github.com/matt1795}{https://github.com/matt1795} & 
	 778-791-4069 \\
\end{tabular*}


%
%--------PROGRAMMING SKILLS------------
\section{Skills \& Tools}
	\resumeSubHeadingListStart
		\item {
				\textbf{Languages}{: C/C++ (proficient), Javascript(proficient),
				Python(proficient), Assembly (occasional use), SQL(occasional
				use), Java (familiar).
				}
		}
		\item {
				\textbf{Technologies}{: Node.js, AWS, MQTT, GraphQL, React \&
				React Native, \LaTeX.}
		}
		\item {
			\textbf{Development Tools}{: Git, JIRA, Confluence.}
		}
	\resumeSubHeadingListEnd




%-----------EXPERIENCE-----------------
\section{Experience}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Full-Stack Engineer}{Oct. 2017 - Present}
			{Plasmatic Technologies Inc.}{Vancouver, BC}
		\resumeItemListStart
			\resumeItem{Firmware}
				{Reverse engineered a proprietary serial communication protocol
				for a home security system by programming an MCU with C to
				handle hardware interface and streamed data over a UART to a PC
				which analyzed packet structure using Python.}
			\resumeItem{Embedded Linux}
				{Built the linux kernel with custom drivers for a touch screen
				display. Implemented a demo GUI using pygame.}
			\resumeItem{Back-End}
				{Became adept at using Node.js and some AWS modules (Cognito,
				DynamoDB, Iot-core, Lambda) in order to develop back-end for
				Plasmatic.}
			\resumeItem{Web and App Front-End}
				{Worked with Graphical Designer to implement part of the
				Web-based UI, and large components of the Mobile App using React
				and React Native respectively.}
		\resumeItemListEnd

		\resumeSubheading
			{R\&D Technician (8 month Co-op and two summers)}{Jan. 2015 - Aug. 2017}
			{Argus Controls Ltd.}{Surrey, BC}
			\resumeItemListStart
				\resumeItem{Retrofitting a Growth Chamber}
					{Replaced the control system of a germination chamber with
					Argus's, tuned the temperature and humidity controllers, and
					added necessary wiring to place testing sensors in chamber.}
				\resumeItem{QA}
					{Validation and verification of sensor accuracy performance
					using retrofitted growth chamber.}
				\resumeItem{Scripting}
					{Used Python to automate the data analysis of sensor
					performance.}
			\resumeItemListEnd

		\resumeSubheading
			{CNC Operator}{Jun. 2013 - Dec. 2014}
			{Redline Manufacturing}{Surrey, BC}
			\resumeItemListStart
				\resumeItem{CNC Mill}
					{Proficiently operated 4-axis CNC Mill.}
				\resumeItem{QA}
					{Inspected part tolerances to ensure meeting requirements
					for ISO-9001 certification.}
				\resumeItem{Maintenance}
					{Cleaned machines, refilled coolant, swept floors -- did
					whatever needed doing to keep the shop running smoothly.}
			\resumeItemListEnd
	\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
	\resumeSubHeadingListStart
		\resumeSubItem{Prosthetics and Orthopedics Monitoring System}
			{Capstone project -- a platform for monitoring the wear
			time of Scoliosis braces for compliance and research purposes.}
		\resumeSubItem{BCIT Sailbot}{An extra-curricular and multi-disciplinary
			project at BCIT to design and build an autonomous sailing robot.}
		\resumeSubItem{cold\_war\_chat}{Designed a communication stack for an 
			RTOS which included AES-128 encryption and a cheap, half-duplex, 
			OOK channel.}
		\resumeSubItem{markov-dictionary}{A graph data structure for storing the
			markov-chain of arbitrary input text. Could be used for analysis or
			text generation.}
		\resumeSubItem{graphics}{A fork of a friend's C-based image drawing
			library, added color channels and a C++ wrapper class.}
		\resumeSubItem{HAM Radio}{Currently studying for HAM Basic license.}
		\resumeSubItem{CNC Router}{A small CNC Router at home to 
			machine woods, plastics, and soft metals.}
		\resumeSubItem{zork-irc}{A small project to hook up Zork, an old text
			based RPG, to an IRC.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Bachelor in Electrical Engineering}{Jan. 2014 -- Jun. 2018}
			{British Columbia Institute of Technology}{Burnaby, BC}
	\resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
