%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Modified by: Matthew Knight
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
		\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{\small#3} & \textit{\small #4} \\
		\end{tabular*}
	\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://sourabhbajaj.com/}{\Large Matthew Knight}} &
		\href{mailto:mgk1795@gmail.com}{mgk1795@gmail.com}\\
	\href{https://github.com/matt1795}{https://github.com/matt1795} & 
	 778-791-4069 \\
\end{tabular*}


%
%--------PROGRAMMING SKILLS------------
\section{}

From my understanding Bluzelle is looking for a talented C++ developer who can
write software in a highly collaborative and test driven environment. I'm an
excellent fit becuase I'm proactive, enjoy working with databases and care about
developing well tested, reliable software.

\vspace{1 em}

I recently graduated from BCIT with a Bachelor in Electrical Engineering and
currently work as a Full Stack Engineer. Having worked from hardware to GUI
design I have found that my passion lies in developing highly reliable and
efficient software. Throughout my degree (and currently still), I worked on
personal projects to further my knowledge and abilities. The most notable
projects are BCIT Sailbot and POMS. Firstly, I started BCIT Sailbot so that I
could engage with other students in different disciplines in order to design and
build an autonomous sailing robot. Secondly POMS (Prosthetic and Orthopedic
Monitoring System) is a full-stack IoT platform that involved designing a
low-power wear-time sensor, a BLE gateway, a back-end based on PostgreSQL and
node.js, and React front-end. This project was originally my capstone, but my
team and I are continuing the work with our sponsor, Hodgson Orthopedic Group,
to use the system for Scoliosis research.

\vspace{1 em}
I've worked at Plasmatic Technologies since last October, working two days a
week on top of my full course load and transitioned to a full-time position in
June. One of the greatest lessons I've taken from Plasmatic is the importance of
testing in order to create reliable production code. Having worked at a number
of levels in the stack, I've found that my passion lies in C++ development
because I enjoy the challenges associated with memory management,
multithreading, and networking.

\vspace{1 em}
Through work and projects, I've gained some experience with SQL and noSQL
databases as both a system designer and application developer. One of the things
I've been curious about is horizontal scaling of these systems and I really
liked SwarmDB's approach by utilizing blockchain technology. I would very much
likst to be part of bringing this technology to fruition. 

\vspace{1 em}

I think that I have a lot to contribute to Bluzelle. It would be my pleasure
if we could meet up and talk further about my qualifications for this position.
You can contact me by phone at 778-791-4069; or by e-mail mgk1795@gmail.com.

\vspace{1 em}
Cheers,

Matt Knight

\end{document}
